The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
No message

The key explanatory variable will be the degree of self confidence. We will compute an index from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

@@

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.

3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.

@@

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007). Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

@@

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities. Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996). We will explore further the way this mechanism works. Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009). We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.

Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different. They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes. We believe there is a more widely spread systematic effect of cultural and educational patterns. David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect. Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.

Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism. Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts. More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively. All these will be precious on the way.

Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large. Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002). Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.

>>>>

The key explanatory variable will be the degree of self confidence as an index that we will compute from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).

@@

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.

3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.

@@

What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors. However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007]. Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

@@

This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities. More specifically, we intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
